---
title: "15L group project"
author: "Hongtao Qian"
date: "2022/2/15"
output:
  html_document: 
    keep_md: yes
    theme: spacelab
---

## Seed Variability
The data set used here is on [New Phytologist](https://nph.onlinelibrary.wiley.com/doi/10.1111/nph.16617). Pearse, I.S., LaMontagne, J.M., Lordon, M., Hipp, A.L. and Koenig, W.D. (2020), Biogeography and phylogeny of masting: do global patterns fit functional hypotheses?. New Phytol, 227: 1557-1567. 
```{r}
library(tidyverse)
library(skimr)
library(ggplot2)
library(here)
library(janitor)
```

1. Data load from the original CSV file. 
```{r}
seed <- read.csv(here("project", "data", "interannual_variability.csv"))%>%
  clean_names()%>%
  select(!contains("sd_"))%>%
  select(!contains("acf"))%>%
  select(!contains("mid"))%>%
  select(!contains("long"))
skim(seed)
```
2. Data tidy up to change the information of latitude to different types of regions. 
```{r}
seed <- seed%>%
  mutate(region=case_when(-23.5<=latitude & latitude<=23.5~"Tropical", 
                          23.5<latitude | -23.5>latitude~"Temperate", 
                          ))
head(seed, n=5)
```


3. Take the glimpse of the relationship between variability of seed crops (cv) and latitude or variability of annual precipitation (cv_precip_annual). 
```{r}
seed %>%
  ggplot(aes(x=latitude, y=cv))+
  xlim(0, 65)+
  geom_point()+
  geom_smooth(se=F)
```

```{r}
seed %>%
  ggplot(aes(x=cv_precip_annual, y=cv))+
  geom_point()+
  geom_smooth(se=F)
```
#### This comparison does not indicate a strong relationship. 

4. Make a comparision between variability of seed crops (cv) and variability of seasonal precipitation (cv_precip_spring & cv_precip_summer). 
```{r}
seed %>%
  select(cv, cv_precip_spring, cv_precip_summer, region, pollination_type, seed_dispersal_type)%>%
  rename(spring = cv_precip_spring, summer=cv_precip_summer)%>%
  pivot_longer(cols = c("spring", "summer"),
                 values_to = "cv_precip", 
               names_to = "season")%>%
  ggplot(aes(x=cv_precip, y=cv, color=season))+
  geom_point(alpha=.2)+
  geom_smooth(se=F)
```

5. It's time to determine the relationship between variability of seed crops (cv) and some characteristics among plant species. 
```{r}
seed %>%
  group_by(pollination_type)%>%
  ggplot(aes(x=pollination_type, y=cv, fill=pollination_type))+
  geom_boxplot()+
  facet_grid(seed_dispersal_type~lifeform)
```

6. Intergenus comparison to examine whether there is a relationship between variability of seed crops (cv) and genus. Just choose three genus with the most series. 
```{r}
seed%>%
  group_by(genus)%>%
  summarise(type=n_distinct(species))%>%
  arrange(desc(type))
```
```{r}
seed%>%
  filter(genus == "QUERCUS" | genus == "PINUS" | genus == "CHIONOCHLOA")%>%
  ggplot(aes(x=genus, y=cv, fill=genus))+
  geom_boxplot()
```
```{r}
seed%>%
  filter(genus == "QUERCUS" | genus == "PINUS" | genus == "CHIONOCHLOA")%>%
  ggplot(aes(x=latitude, fill=genus))+
  geom_density(alpha=.2)
```


