---
title: "15L group project"
author: "Hongtao Qian"
date: "2022/2/15"
output:
  html_document: 
    keep_md: yes
    theme: spacelab
---

## Seed Variability
The data set used here is on [New Phytologist](https://nph.onlinelibrary.wiley.com/doi/10.1111/nph.16617). Pearse, I.S., LaMontagne, J.M., Lordon, M., Hipp, A.L. and Koenig, W.D. (2020), Biogeography and phylogeny of masting: do global patterns fit functional hypotheses?. New Phytol, 227: 1557-1567. 
```{r}
library(tidyverse)
library(skimr)
library(ggplot2)
library(here)
library(janitor)
library(ggmap)
library(shiny)
library(shinydashboard)
```

1. Data load from the original CSV file. 
```{r}
seed <- read.csv(here("project", "data", "interannual_variability.csv"))%>%
  clean_names()
names(seed)
summary(seed$cv)
```
2. Data tidy up to change the information of latitude to different types of regions. 
```{r}
seed <- seed%>%
  mutate(production=case_when(cv <= 0.8936 ~"Low", 
                          0.8936 <= cv & cv <= 1.17 ~"Medium Low",
                          1.17 <= cv & cv <= 1.5132 ~"Medium High",
                          1.5132 <= cv ~"High"
                          ))
head(seed, n=5)
```


3. Take the glimpse of the relationship between variability of seed crops (cv) and latitude or variability of annual precipitation (cv_precip_annual). 
```{r}
lat <- c(-46.3, 65.9)
long <- c(-148.1, 176.5)
bounding <- make_bbox(long, lat, f = 0.05)
seed_map <- get_map(bounding, style = "watercolor", source = "stamen")
ggmap(seed_map)+
  geom_point(data=seed, aes(longitude, latitude, color = production))
seed%>%
  filter(hemisphere == "N")%>%
  ggplot(aes(x=latitude, y=cv))+
  geom_point()+
  geom_smooth(se=F)+
  facet_wrap(~hemisphere, scales = "free")
```

```{r}
seed %>%
  ggplot(aes(x=cv_precip_annual, y=cv))+
  geom_point()+
  geom_smooth(se=F)
```
#### This comparison does not indicate a strong relationship. 

4. Make a comparision between variability of seed crops (cv) and variability of seasonal precipitation (cv_precip_spring & cv_precip_summer). 
```{r}
seed %>%
  select(cv, cv_precip_spring, cv_precip_summer, region, pollination_type, seed_dispersal_type)%>%
  rename(spring = cv_precip_spring, summer=cv_precip_summer)%>%
  pivot_longer(cols = c("spring", "summer"),
                 values_to = "cv_precip", 
               names_to = "season")%>%
  ggplot(aes(x=cv_precip, y=cv, color=season))+
  geom_point(alpha=.2)+
  geom_smooth(se=F)
```

5. It's time to determine the relationship between variability of seed crops (cv) and some characteristics among plant species. 
```{r}
seed %>%
  group_by(pollination_type)%>%
  ggplot(aes(x=pollination_type, y=cv, fill=pollination_type))+
  geom_boxplot()+
  facet_wrap(~seed_dispersal_type)
```

6. Intergenus comparison to examine whether there is a relationship between variability of seed crops (cv) and genus. Just choose three genus with the most series. 
```{r}
seed%>%
  group_by(genus)%>%
  summarise(type=n_distinct(species))%>%
  arrange(desc(type))
```
```{r}
seed%>%
  filter(genus == "QUERCUS" | genus == "PINUS" | genus == "ABIES")%>%
  ggplot(aes(x=genus, y=cv, fill=genus))+
  geom_boxplot(alpha=.3)+
  geom_violin(alpha=.2)
```
```{r}
seed%>%
  filter(genus == "QUERCUS" | genus == "PINUS" | genus == "ABIES")%>%
  ggplot(aes(x=latitude, fill=genus))+
  geom_density(alpha=.2)
```

7. Just make an app. 
```{r}
ui <- dashboardPage(
  dashboardHeader(title = "Variability of Annual Seed Production"),
  dashboardSidebar(disable = T),
  dashboardBody(
  fluidRow(
  box(title = "Plot Options", width = 3,
  selectInput("x", "x-axis Option", choices = c("sd_tmax_annual","sd_tmin_annual","sd_tmax_summer","sd_tmin_summer","sd_tmax_spring", "sd_tmin_spring", "cv_precip_annual", "cv_precip_spring", "cv_precip_summer"),
              selected = "International"),
  ),
  box(title = "Plot of Seed Production Variability Versus Different Factors", width = 7,
  plotOutput("plot", width = "600px", height = "500px")
  )
  )
  ) 
) 

server <- function(input, output, session) { 
  output$plot <- renderPlot({seed %>% 
  ggplot(aes_string(x = input$x, y="cv")) +
  geom_point(fill = "tomato", alpha = 0.8)+
  geom_smooth(se=F)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  labs(x=input$x, 
       y="Seed Production Variability")
  })
  session$onSessionEnded(stopApp)
  }

shinyApp(ui, server)
```



